---
format: html
editor: visual
---

# Homework 9

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(lubridate)
library(corrplot)
library(gridExtra)
library(baguette)
library(parsnip)
library(ranger)
library(vip)

```

### Read Data

```{r, message=FALSE, echo=FALSE}
soul_bikes <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/SeoulBikeData.csv",
                        locale = locale(encoding = "latin1"))

names(soul_bikes)

#Transform:
#- dates to datetime formats
#- snake_case vars
# Clean and transform the data
soul_bikes_clean <- soul_bikes |>
  clean_names() |>  # This will convert "Functioning Day" to "functioning_day"
  mutate(
    date = dmy(date),
    seasons = as.factor(seasons),
    holiday = as.factor(holiday),
    functioning_day = as.factor(functioning_day)
  )


# Check column names to verify
names(soul_bikes_clean)

# Then filter
soul_bikes_functioning <- soul_bikes_clean[soul_bikes_clean$functioning_day == "Yes", ]
```

## Basic EDA
### Check for missing values
### Create Summary Stats for Numerics and Character/Factor variables
### Create Daily Summary means and totals
```{r}
#Basic EDA
#Missing values
missing_summ <- soul_bikes |>
  summarize(across(everything(), \(x) sum(is.na(x)))) |>
  pivot_longer(everything(),
                names_to = "variable",
                values_to = "missing_count")
missing_summ

#By variable summary stats for numerics
bike_summ_nums <- soul_bikes_functioning |>
  select(where(is.numeric)) |>
  summarize(across(everything(),
                   list(
                     mean = \(x) mean(x, na.rm = TRUE),
                     sd = \(x) sd(x, na.rm = TRUE),
                     median = \(x) median(x, na.rm = TRUE),
                     iqr = \(x) IQR(x, na.rm = TRUE),
                     min = \(x) min(x, na.rm = TRUE),
                     max = \(x) max(x, na.rm = TRUE),
                     n_missing = \(x) sum(is.na(x))
                   ))) |>
              pivot_longer(
                everything(),
                names_to = c("column", "stat"),
                names_pattern = "(.*)_(.*)",
                values_to = "values"
              )

#By variable summary stats for character/factor
bike_summ_cats <- soul_bikes_functioning |>
  select(where(is.character), where(is.factor)) |>
  summarize(across(everything(),
    list(
      n_unique = \(x) n_distinct(x),
      n_missing = \(x) sum(is.na(x))
    )
  )) |>
  pivot_longer(
    everything(),
    names_to = c("column", "stat"),
    names_pattern = "(.*)_(.*)",
    values_to = "value"
  )

# Factor levels summary
factor_levels <- soul_bikes_functioning |>
  select(where(is.factor), where(is.character)) |>
  summarize(across(everything(), \(x) list(sort(unique(x))))) |>
  pivot_longer(
    everything(),
    names_to = "column",
    values_to = "levels"
  ) |>
  mutate(
    n_levels = map_int(levels, length),
    levels = map_chr(levels, toString)
  )

#7. Summarize across hours
daily_summ <- soul_bikes_functioning |>
  group_by(date, seasons, holiday) |>
  summarize(
    #totals
    total_bikes = sum(rented_bike_count),
    total_rainfall = sum(rainfall_mm),
    total_snowfall = sum(snowfall_cm),

    #weather means
    avg_temp = mean(temperature_c),
    avg_humidity = mean(humidity_percent),
    avg_wind_speed = mean(wind_speed_m_s),
    avg_visibility = mean(visibility_10m),
    avg_dew_point = mean(dew_point_temperature_c),
    avg_solar_rad = mean(solar_radiation_mj_m2),
    .groups = "drop"  # Drop grouping after summary
  )
daily_summ

#Summaries of numerics
bike_summ_nums <- daily_summ |>
  select(where(is.numeric)) |>
  summarize(across(everything(),
                   list(
                     mean = \(x) mean(x, na.rm = TRUE),
                     sd = \(x) sd(x, na.rm = TRUE),
                     median = \(x) median(x, na.rm = TRUE),
                     iqr = \(x) IQR(x, na.rm = TRUE),
                     min = \(x) min(x, na.rm = TRUE),
                     max = \(x) max(x, na.rm = TRUE),
                     n_missing = \(x) sum(is.na(x))
                   ))) |>
  pivot_longer(
    everything(),
    names_to = c("column", "stat"),
    names_pattern = "(.*)_(.*)",
    values_to = "values"
  )
bike_summ_nums
```

## Plots
#### Calculate Correlation Matrix 
#### Create Plots for top 4 correlations
```{r}
# Calculate correlation matrix
cor_matrix <- daily_summ |>
  select(total_bikes, avg_temp, avg_humidity, avg_wind_speed,
         avg_visibility, avg_solar_rad, total_rainfall, total_snowfall) |>
  cor(use = "complete.obs")
cor_matrix
# Create correlation plot
corrplot(cor_matrix,
         method = "color",
         type = "upper",
         addCoef.col = "black",
         tl.col = "black",
         tl.srt = 45,
         diag = FALSE)

# Individual scatter plots with trend lines
temp_v_rentals <- ggplot(daily_summ, aes(x = avg_temp, y = total_bikes)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", color = "red") +
  labs(title = "Temperature vs Bike Rentals",
       x = "Average Temperature (°C)",
       y = "Total Daily Rentals") +
  theme_minimal()

humid_v_rentals <- ggplot(daily_summ, aes(x = avg_humidity, y = total_bikes)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", color = "blue") +
  labs(title = "Humidity vs Bike Rentals",
       x = "Average Humidity (%)",
       y = "Total Daily Rentals") +
  theme_minimal()

sun_v_rentals <- ggplot(daily_summ, aes(x = avg_solar_rad, y = total_bikes)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", color = "orange") +
  labs(title = "Solar Radiation vs Bike Rentals",
       x = "Average Solar Radiation (MJ/m2)",
       y = "Total Daily Rentals") +
  theme_minimal()

vis_v_rentals <- ggplot(daily_summ, aes(x = avg_visibility, y = total_bikes)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", color = "green4") +
  labs(title = "Visibility vs Bike Rentals",
       x = "Average Visibility (10m)",
       y = "Total Daily Rentals") +
  theme_minimal()

# Arrange plots in a grid

grid.arrange(temp_v_rentals, humid_v_rentals, sun_v_rentals, vis_v_rentals, ncol = 2)
```

## MLR
### Fit a Multiple Linear Regression Model using 3 specified Recipes
```{r,  message=FALSE, echo=FALSE}
#Split the data
set.seed(123)
bike_split <- initial_split(daily_summ,
                            prop = 0.75,
                            strata = seasons)

trn <- training(bike_split)
tst <- testing(bike_split)
folds <- vfold_cv(trn, v = 10, strata = seasons)


#Fitting MLR Models
#Recipe 1
recipe_1 <- recipe(total_bikes ~ ., data = trn) |>
  update_role(date, new_role = "ID") |>
  # Extract day of week and create weekend factor
  step_date(date, features = "dow") |>
  step_mutate(
    weekend = factor(
      if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
      levels = c("weekday", "weekend")  # explicitly set levels
    )
  ) |>
  # Remove the intermediate date_dow variable
  step_rm(date_dow) |>
  # Standardize numeric variables
  step_normalize(all_numeric_predictors()) |>
  # Create dummy variables
  step_dummy(all_nominal_predictors())


recipe_1 |>
  prep() |>
  bake(new_data = NULL) |>
  glimpse()


#Recipe 2
recipe_2 <- recipe(total_bikes ~ ., data = trn) |>
  update_role(date, new_role = "ID") |>
  step_date(date, features = "dow") |>
  step_mutate(
    weekend = factor(
      if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
      levels = c("weekday", "weekend")
    )
  ) |>
  step_rm(date_dow) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors()) |>
  # Changed interaction syntax to use explicit formulas
  step_interact(terms = ~ starts_with("seasons_"):starts_with("holiday_")) |>
  step_interact(terms = ~ starts_with("seasons_"):avg_temp) |>
  step_interact(terms = ~ total_rainfall:avg_temp)

recipe_2 |>
  prep() |>
  bake(new_data = NULL) |>
  glimpse()

#Recipe 3

recipe_3 <- recipe(total_bikes ~ ., data = trn) |>
  update_role(date, new_role = "ID") |>
  step_date(date, features = "dow") |>
  step_mutate(
    weekend = factor(
      if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
      levels = c("weekday", "weekend")
    )
  ) |>
  step_rm(date_dow) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors()) |>
  # Modify interaction specification to use separate terms=
  step_interact(terms = ~ starts_with("seasons_") * starts_with("holiday_") +
                  starts_with("seasons_") * avg_temp +
                  total_rainfall * avg_temp) |>
  step_poly(total_rainfall, avg_temp, avg_humidity, avg_wind_speed,
            avg_visibility, avg_dew_point, avg_solar_rad,
            degree = 2)

recipe_3 |>
  prep() |>
  bake(new_data = NULL) |>
  glimpse()


#setup LM engine
# Set up linear model specification
lm_spec <- linear_reg() |>
  set_engine("lm")

# Create workflows for each recipe
workflow_1 <- workflow() |>
  add_recipe(recipe_1) |>
  add_model(lm_spec)

workflow_2 <- workflow() |>
  add_recipe(recipe_2) |>
  add_model(lm_spec)

workflow_3 <- workflow() |>
  add_recipe(recipe_3) |>
  add_model(lm_spec)

# Fit models using 10-fold CV
cv_fit_1 <- workflow_1 |>
  fit_resamples(
    resamples = folds,
    metrics = metric_set(rmse)
  )

cv_fit_2 <- workflow_2 |>
  fit_resamples(
    resamples = folds,
    metrics = metric_set(rmse)
  )

cv_fit_3 <- workflow_3 |>
  fit_resamples(
    resamples = folds,
    metrics = metric_set(rmse)
  )

# Compare CV results
cv_results <- bind_rows(
  collect_metrics(cv_fit_1) |> mutate(model = "Model 1"),
  collect_metrics(cv_fit_2) |> mutate(model = "Model 2"),
  collect_metrics(cv_fit_3) |> mutate(model = "Model 3")
) |>
  arrange(mean)

print(cv_results)


#Model 3 is best fit
# Use last_fit with the best model (Model 3)
final_fit <- workflow_3 |>
  last_fit(bike_split)

# Get test set metrics
collect_metrics(final_fit)

# Get coefficients
final_fit |>
  extract_fit_parsnip() |>
  tidy()
```


## LASSO Model
### Re-import data to align with variable names chosen for hw9
```{r,  message=FALSE, echo=FALSE}
bike_data <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/SeoulBikeData.csv",
                      locale = locale(encoding = "latin1")) |>
  clean_names() |>
  mutate(
    date = dmy(date),
    seasons = as.factor(seasons),
    holiday = as.factor(holiday),
    functioning_day = as.factor(functioning_day)
  ) |>
  filter(functioning_day == "Yes")

# Create summaries
bike_data <- bike_data |>
  group_by(date, seasons, holiday) |>
  summarize(
    total_bikes = sum(rented_bike_count),
    total_rainfall = sum(rainfall_mm),
    total_snowfall = sum(snowfall_cm),
    avg_temp = mean(temperature_c),
    avg_humidity = mean(humidity_percent),
    avg_wind_speed = mean(wind_speed_m_s),
    avg_visibility = mean(visibility_10m),
    avg_dew_point = mean(dew_point_temperature_c),
    avg_solar_rad = mean(solar_radiation_mj_m2),
    .groups = "drop"
  )

# Split data
set.seed(123)
bike_split <- initial_split(bike_data, prop = 0.75, strata = seasons)
bike_train <- training(bike_split)
bike_test <- testing(bike_split)
bike_cv_folds <- vfold_cv(bike_train, v = 10, strata = seasons)


lasso_recipe <- recipe(total_bikes ~ ., data = bike_train) |>
  update_role(date, new_role = "ID") |>
  step_date(date, features = "dow") |>
  step_mutate(
    weekend = factor(
      if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
      levels = c("weekday", "weekend")
    )
  ) |>
  step_rm(date_dow) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors()) |>
  step_interact(terms = ~ starts_with("seasons_") * starts_with("holiday_") +
                  starts_with("seasons_") * avg_temp +
                  total_rainfall * avg_temp) |>
  step_poly(avg_temp, avg_humidity, avg_wind_speed, 
            avg_visibility, avg_dew_point, avg_solar_rad,
            degree = 2)

# LASSO model specification
lasso_spec <- linear_reg(penalty = tune(), mixture = 1) |>
  set_engine("glmnet")

# Create workflow
lasso_wkf <- workflow() |>
  add_recipe(lasso_recipe) |>
  add_model(lasso_spec)

# Tune LASSO
lasso_grid <- lasso_wkf |>
  tune_grid(
    resamples = bike_cv_folds,
    grid = grid_regular(penalty(), levels = 100),
    metrics = metric_set(rmse, mae)
  )

# Get best LASSO model
#pull out best model with select_best() and finalize_workflow()
lasso_lowest_rmse <- select_best(lasso_grid, metric = "rmse")
lasso_final <- finalize_workflow(lasso_wkf, lasso_lowest_rmse)

#Fit to training data
lasso_final_fitted <- finalize_workflow(lasso_wkf, lasso_lowest_rmse) |>
  fit(bike_train)

tidy(lasso_final_fitted)
#Fit to full training + test + get fit + performance metrics
lasso_fit <- last_fit(lasso_final, bike_split)
```

## Regression Tree
```{r,  message=FALSE, echo=FALSE}
bike_data <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/SeoulBikeData.csv",
                      locale = locale(encoding = "latin1")) |>
  clean_names() |>
  mutate(
    date = dmy(date),
    seasons = as.factor(seasons),
    holiday = as.factor(holiday),
    functioning_day = as.factor(functioning_day)
  ) |>
  filter(functioning_day == "Yes")

# Create daily summaries
bike_data <- bike_data |>
  group_by(date, seasons, holiday) |>
  summarize(
    total_bikes = sum(rented_bike_count),
    total_rainfall = sum(rainfall_mm),
    total_snowfall = sum(snowfall_cm),
    avg_temp = mean(temperature_c),
    avg_humidity = mean(humidity_percent),
    avg_wind_speed = mean(wind_speed_m_s),
    avg_visibility = mean(visibility_10m),
    avg_dew_point = mean(dew_point_temperature_c),
    avg_solar_rad = mean(solar_radiation_mj_m2),
    .groups = "drop"
  )

# Split data
set.seed(123)
bike_split <- initial_split(bike_data, prop = 0.75, strata = seasons)
bike_train <- training(bike_split)
bike_test <- testing(bike_split)
bike_cv_folds <- vfold_cv(bike_train, v = 10, strata = seasons)


#2. Setup recipes for data model
tree_rec <- recipe(total_bikes ~ ., data = bike_train) |>
  update_role(date, new_role = "ID") |>
  step_date(date, features = "dow") |>
  step_mutate(
    weekend = factor(
      if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
      levels = c("weekday", "weekend")
    )
  ) |>
  step_rm(date_dow) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors())

# 3. Set up model type and engine
tree_mod <- decision_tree(tree_depth = tune(),
                          min_n = 20,
                          cost_complexity = tune()) |>
  set_engine("rpart") |>
  set_mode("regression")

# 4. Create workflows
tree_wkf <- workflow() |>
  add_recipe(tree_rec) |>
  add_model(tree_mod)



#manually specify how many of each tuning parameter you want with grid_regular
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = c(10,5))


# 5. Fit to CV folds. Use tune_grid() to fit models

tree_cv_fit <- tree_wkf |>
  tune_grid(resamples = bike_cv_folds,
            grid = tree_grid)

tree_cv_fit |>
  collect_metrics()


#plot
tree_cv_fit %>%
  collect_metrics() %>%
  mutate(tree_depth = factor(tree_depth)) %>%
  ggplot(aes(cost_complexity, mean, color = tree_depth)) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) +
  scale_x_log10(labels = scales::label_number()) +
  scale_color_viridis_d(option = "plasma", begin = .9, end = 0)

#sort by smallest RMSE
tree_cv_fit |>
  collect_metrics() |>
  filter(.metric == "rmse") |>
  arrange(mean)

#select best to select best model's tuning parameter values and metric specification
tree_best_params <- select_best(tree_cv_fit, metric = "rmse")
tree_best_params

#finalize workflow model on the training set with finalize_workflow
tree_final_wkf <- tree_wkf |>
  finalize_workflow(tree_best_params)

tree_final_fit <- tree_final_wkf |>
  last_fit(bike_split)
tree_final_fit

tree_final_fit |>
  collect_metrics()

tree_final_model <- extract_workflow(tree_final_fit)
tree_final_model

tree_final_model |>
  extract_fit_engine() |>
  rpart.plot::rpart.plot(roundint = FALSE)

```


##  BAGGED Tree
```{r,  message=FALSE, echo=FALSE}
# Set recipe 
bag_rec <- recipe(total_bikes ~ ., data = bike_train) |>
 update_role(date, new_role = "ID") |>
 step_date(date, features = "dow") |>
 step_mutate(
   weekend = factor(
     if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
     levels = c("weekday", "weekend")
   )
 ) |>
 step_rm(date_dow) |>
 step_normalize(all_numeric_predictors()) |>
 step_dummy(all_nominal_predictors())

# Set model
bag_spec <- bag_tree(
 tree_depth = 5, 
 min_n = 10,
 cost_complexity = tune()
) |>
 set_engine("rpart") |>
 set_mode("regression")

# Create workflow
bag_wkf <- workflow() |>
 add_recipe(bag_rec) |>
 add_model(bag_spec) 

# Tune model
bag_fit <- bag_wkf |>
 tune_grid(
   resamples = bike_cv_folds,
   grid = grid_regular(cost_complexity(), levels = 15),
   metrics = metric_set(rmse, mae)
 )

# Get metrics
bag_fit |>
 collect_metrics() |>
 filter(.metric == "rmse") |>
 arrange(mean)

# Get best parameters
bag_best_params <- select_best(bag_fit, metric = "rmse")

# Finalize workflow
bag_final_wkf <- bag_wkf |>
 finalize_workflow(bag_best_params)

# Final fit and evaluation  
bag_final_fit <- bag_final_wkf |>
 last_fit(bike_split, metrics = metric_set(rmse, mae))
```


## Random Forest
```{r,  message=FALSE, echo=FALSE}
rf_rec  <- recipe(total_bikes ~ ., data = bike_train) |>
 update_role(date, new_role = "ID") |>
 step_date(date, features = "dow") |>
 step_mutate(
   weekend = factor(
     if_else(date_dow %in% c("Sat", "Sun"), "weekend", "weekday"),
     levels = c("weekday", "weekend")
   )
 ) |>
 step_rm(date_dow) |>
 step_normalize(all_numeric_predictors()) |>
 step_dummy(all_nominal_predictors())

# Specify model with tuning
rf_spec <- rand_forest(mtry = tune()) |>  
  set_engine("ranger", importance = "permutation") |>
  set_mode("regression")

# Create workflow  
rf_wkf <- workflow() |>
  add_recipe(rf_rec) |>
  add_model(rf_spec)

# Tune model with cross validation
rf_fit <- rf_wkf |>
  tune_grid(
    resamples = bike_cv_folds,
    grid = tibble(mtry = c(1, 2)),
    metrics = metric_set(rmse, rsq)
  )

# Get best parameters
rf_best_params <- select_best(rf_fit, metric = "rmse")

# Finalize workflow with best parameters
rf_final_wkf <- rf_wkf |>
  finalize_workflow(rf_best_params)

# Fit final model
rf_final_fit <- rf_final_wkf |>
  last_fit(bike_split)

# Extract final model if needed
rf_final_model <- rf_final_fit |>
  extract_fit_parsnip()
```

## Compare Models
```{r}
# 1. Final fits for each model type
mlr_final_fit <- workflow_3 |> 
  last_fit(bike_split, metrics = metric_set(rmse, mae))

lasso_final_fit <- lasso_wkf |>
  finalize_workflow(lasso_lowest_rmse) |>
  last_fit(bike_split, metrics = metric_set(rmse, mae))

tree_final_fit <- tree_final_wkf |>
  last_fit(bike_split, metrics = metric_set(rmse, mae))

bag_final_fit <- bag_final_wkf |>
  last_fit(bike_split, metrics = metric_set(rmse, mae, rsq))

rf_final_fit <- rf_final_wkf |>
  last_fit(bike_split, metrics = metric_set(rmse, mae))

# 2. Create comparison dataframes
final_metrics <- tibble(
    model = c("MLR", "LASSO", "Regression Tree", "Bagged Tree", "Random Forest"),
    rmse = c(
        mlr_final_fit |> collect_metrics() |> filter(.metric == "rmse") |> pull(.estimate),
        lasso_final_fit |> collect_metrics() |> filter(.metric == "rmse") |> pull(.estimate),
        tree_final_fit |> collect_metrics() |> filter(.metric == "rmse") |> pull(.estimate),
        bag_final_fit |> collect_metrics() |> filter(.metric == "rmse") |> pull(.estimate),
        rf_final_fit |> collect_metrics() |> filter(.metric == "rmse") |> pull(.estimate)
    )
)

final_mae <- tibble(
    model = c("MLR", "LASSO", "Regression Tree", "Bagged Tree", "Random Forest"),
    mae = c(
        mlr_final_fit |> collect_metrics() |> filter(.metric == "mae") |> pull(.estimate),
        lasso_final_fit |> collect_metrics() |> filter(.metric == "mae") |> pull(.estimate),
        tree_final_fit |> collect_metrics() |> filter(.metric == "mae") |> pull(.estimate),
        bag_final_fit |> collect_metrics() |> filter(.metric == "mae") |> pull(.estimate),
        rf_final_fit |> collect_metrics() |> filter(.metric == "mae") |> pull(.estimate)
    )
)

# 3. Combine metrics
cat("### RMSE by Model")
knitr::kable(final_metrics)

cat("### MAE by Model")
knitr::kable(final_mae)

cat("### Combined Performance Metrics")
final_comparison <- final_metrics %>%
  left_join(final_mae, by = "model")
knitr::kable(final_comparison)

```

## Summarize Models
### Models of MLR, LASSO, Regression Tree, Bagged Tree, and Random Forest were compared againt the Seoul Bike Data data set
### Models were tuned by 10-fold cross-validation

### Conclusion: MLR 3 model provided the best fit of all models assessed against the metric of RMSE: 2913 and MAE: 2202
```{r}
# 1. Final coefficient tables for LASSO and MLR
mlr_coef <- mlr_final_fit |>
  extract_fit_parsnip() |>
  tidy() |>
  knitr::kable()

lasso_coef <- lasso_final_fit |>
  extract_fit_parsnip() |>
  tidy()  |>
  knitr::kable()

# 2. Plot regression tree
tree_plot <- tree_final_model |>
  extract_fit_engine() |>
  rpart.plot::rpart.plot(roundint = FALSE, main = "Regression Tree Final Model")

# 3. Variable importance plots
# For bagged trees
bag_final_model <- bag_final_fit |>
  extract_fit_parsnip()

bag_importance <- bag_final_model |>
  extract_fit_engine() |>
  var_imp() |>
  mutate(term = factor(term, levels = term)) |>
  ggplot(aes(x = term, y = value)) +
  geom_col() +
  coord_flip() +
  labs(title = "Bagged Trees Variable Importance",
       x = "Variable",
       y = "Importance")
# For random forest 
rf_final_model <- rf_final_fit |>
  extract_fit_parsnip()

rf_importance <- vip(rf_final_model) +
  labs(title = "Random Forest Variable Importance")

# Display plots
print(bag_importance)
print(rf_importance)

# 4. Show coefficients
knitr::kable(mlr_coef)

knitr::kable(lasso_coef)

# 5. Fit best model to entire dataset
best_model <- workflow_3 |>
  fit(bike_data)

best_model |>
  extract_fit_parsnip() |>
  tidy() |>
  knitr::kable()
```

